Church Bells are Not Ringing: Decrease in the Opposite-Sex and Same-Sex Couples Opting for Religious Marriage Ceremonies in England and Wales

### 2024-04-25 paper/paper.qmd
final paper and references upload

ten_year <- subset(opposite_sex, year >= 2011 & year <= 2020)
ggplot(ten_year, aes(x = year)) + 
  geom_line(aes(y = coe), color = "darkred") + 
  geom_line(aes(y = rc), color = "yellow")  +
  geom_line(aes(y = other_christian), color="darkgreen")  +
  geom_line(aes(y = other_religion), color="darkviolet")  +
  theme_minimal() +
  scale_x_continuous(breaks = seq(2011, 2020, 1)) +
  scale_y_continuous(breaks = seq(0, 60000, 5000))+
  labs(x = "Year", y = "Number of Ceremonies Conducted")
```

@@

same_sex_demographics <-
  pivot_longer(same_sex, cols = c(male, female), names_to = "Sex", values_to = "Count")

@@

## Implication: Fewer Citizens Identify as Christian
Interestingly, the marriage ceremony data analysed and discussed in this paper also indicate that Christianity is becoming less popular or prominent in the lives of English and Welsh citizens. As seen in @fig-oppositereligioustypes, all sects of Christianity have experienced a decrease in the annual number of marriage ceremonies conducted. This implies that fewer couples are religiously involved in Christianity to the extent of including it in their marriage plans.

Looking at "Religion, England and Wales: Census 2021" from the *Office for National Statistics* provides further insight into whether or not religious identification and marriage ceremony type are congruent in their data. In the 2021 census, 46.2% (27.5 million) identified as Christian in comparison to 59.3% (33.3 million) in 2011 [@census2021]. Although Christianity remains the most popular religion in England and Wales, the decrease over a decade is still somewhat significant as less than half the population now identifies as Christian. This is reflected on a smaller level in the opposite-sex marriage ceremony data, as seen in @fig-oppositereligiousten, since all Christian sects experienced a decline in annual marriage ceremonies with the Church of England seeing a reduction of just under 40,000 ceremonies in 2020 compared to 2011.

>>>>

ten_year <- subset(opposite_sex, year >= 2011 & year <= 2020)

ggplot(ten_year, aes(x = year)) + 
  geom_line(aes(y = coe), color = "darkred") + 
  geom_line(aes(y = rc), color = "yellow")  +
  geom_line(aes(y = other_christian), color="darkgreen")  +
  geom_line(aes(y = other_religion), color="darkviolet")  +
  theme_minimal() +
  scale_x_continuous(breaks = seq(2011, 2020, 1)) +
  scale_y_continuous(breaks = seq(0, 60000, 5000))+
  labs(x = "Year", y = "Number of Ceremonies Conducted")
```

@@

# Code referenced from: https://tidyr.tidyverse.org/reference/pivot_longer.html
same_sex_demographics <-
  pivot_longer(same_sex, cols = c(male, female), names_to = "Sex", values_to = "Count")

@@

## Implication: Fewer Citizens Identify as Christian
Interestingly, the marriage ceremony data analysed and discussed in this paper also indicate that Christianity is becoming less popular or prominent in the lives of English and Welsh citizens. As seen in @fig-oppositereligioustype, all sects of Christianity have experienced a decrease in the annual number of marriage ceremonies conducted. This implies that fewer couples are religiously involved in Christianity to the extent of including it in their marriage plans.

Looking at "Religion, England and Wales: Census 2021" from the *Office for National Statistics* provides further insight into whether or not religious identification and marriage ceremony type are congruent in their data. In the 2021 census, 46.2% (27.5 million) identified as Christian in comparison to 59.3% (33.3 million) in 2011 [@census2021]. Although Christianity remains the most popular religion in England and Wales, the decrease over a decade is still somewhat significant as less than half the population now identifies as Christian. This is reflected on a smaller level in the opposite-sex marriage ceremony data, as seen in @fig-oppositereligioustypeten, since all Christian sects experienced a decline in annual marriage ceremonies with the Church of England seeing a reduction of just under 40,000 ceremonies in 2020 compared to 2011.
